### 2022-08-15 doc/src/intro.tex
Define extension names Smaia and Ssaia

>>>>

%-----------------------------------------------------------------------
\section{ISA extensions Smaia and Ssaia}

The Advanced Interrupt Architecture (AIA) defines two names for
extensions to the {\RISCV} instruction set architecture (ISA),
one for machine-level execution environments,
and another for supervisor-level environments.
For a machine-level environment, extension \textbf{Smaia} encompasses
all added CSRs and all modifications to interrupt response behavior
that the AIA specifies for a hart, over all privilege levels.
For a supervisor-level environment, extension \textbf{Ssaia} is
essentially the same as Smaia except excluding the machine-level
CSRs and behavior not directly visible to supervisor level.

Extensions Smaia and Ssaia cover only
those AIA features that impact the ISA at a hart.
Although the following are described or discussed
in this document as part of the AIA, they are not implied by
Smaia or Ssaia because the components are categorized as non-ISA:
APLICs, Duo-PLICs, IOMMUs, and any mechanisms for initiating
interprocessor interrupts apart from writing to IMSICs.

As revealed in subsequent chapters, the exact set
of CSRs and behavior added by the AIA, and hence
implied by Smaia or Ssaia, depends on some other factors:
the base ISA's XLEN (RV32 or RV64), whether \mbox{S-mode}
and the hypervisor extension are implemented,
and whether the hart has an IMSIC.
But individual AIA extension names are not
provided for each possible valid subset.
Rather, the different combinations are inferable
from the intersection of features indicated (such as
RV64I + \mbox{S-mode} + Smaia, but without the hypervisor extension).

Software development tools like compilers and assemblers need not
be concerned about whether an IMSIC exists but should just
allow attempts to access the IMSIC CSRs (described in Chapters
\ref{ch:CSRs} and~\ref{ch:IMSIC}) if Smaia or Ssaia is indicated.
Without an actual IMSIC, such attempts may trap,
but that is not a problem for the development tools.
